
\section{Document format}
This document is formatted according to the official specifications: A4 paper
and the Times New Roman font with a size of 12 pt.
The upper, lower, left and right margins are of 2 cm, each paragraph starts
with a 1.5 cm padding, except for the first one, and the row spacing is one
line.
Each chapter starts on a new odd page.

All these settings are contained in the tuiasithesis.sty file which formats the
entire thesis. The \cmdprint{tuiasithesis} package is included using the
\verb?\usepackage{tuiasithesis}? command.

\section{Defining variables}
The title page and the header use some variables that can be overriden,
though it is not really necessary, and some of them must be modified because
they pertain to the thesis' title, author and advisor.
Some of the variables have two values, the first one for Romanian and the
second one for English, while other variables are language independent and have
only one value.
% in both romanian and english, where it is the case.

The following variables should not be modified:
\cmdprint{thesisuniversity}, \cmdprint{thesisfaculty},
\cmdprint{thesisyear}, \cmdprint{thesiscity} and \cmdprint{thesistype}.
The first two variables have two values, while the latter three have a single
value.

There is a single variable with only one value that must be modified, 
\cmdprint{thesisauthorheader}, which will appear in the document header on the
even pages. The other variables all have two values and are:
\cmdprint{thesistitle}, \cmdprint{thesissubtitle} (is optional can be omitted),
\cmdprint{thesisauthor} and \cmdprint{thesisadvisor}.

If the thesis is written only in Romanian or only in English then the second and
the first value, respectively, may be left blank.
Next is an example of setting the thesis title:

\verb?\thesistitle{Model de teza in LaTeX}{Thesis template in LaTeX}?
